### 2013-07-31 0_frontmatter/abstract.tex
Final changes before submission to Alan???

On the one hand, practical applications for POLSAR data processing require the establishment of discrimination measures
  which are to be scalar and statistically consistent.
On the other hand, these same scalar observable quantities need to be naturally representative of the high-dimensional POLSAR data.
At the same time, it is desirable to establish additive and homoskedastic models, which include several consistent measures of distance, for both SAR and POLSAR data, so that the benefits of homoskedastic statistical estimation framework can be studied and realized.

In this thesis, the statistical behaviour of the determinant of POLSAR covariance matrix is explored.
Concurrently, the effects of homoskedasticity on (POL)SAR speckle filtering within the framework of computational and statistical estimation are also extensively studied.

As a result of these studies, the scalar statistical models for the determinant of POLSAR covariance matrix are proposed and validated.
This observable turns out to be very representative of the complex data as it generalizes the SAR intensity towards the multi-dimensional extension.
Similar to the model for SAR intensity, this generic model for POLSAR is shown to be both multiplicative and heteroskedastic.
Consequently, logarithmic transformation is applied onto these types of data converting them into additive and homoskedastic models.
From these models, several additive measures of distance are proposed for both SAR and POLSAR data.

There are several beneficial implications of the theory proposed in this thesis. 
Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity, its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
Similarly, the homoskedastic model carries additional benefits.
For inexperienced researchers (such as this author when he began this research),
  who attempt to process either SAR or POLSAR data using existing computation algorithms
  which most of the time expect an additive and homoskedastic input,
  this thesis proposes alternative and more familiar additive and homoskedastic models. These replace
 the original ones which are multiplicative and heteroskedastic.
For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 
  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the (POL)SAR statistical estimation framework.

>>>>

SAR and POLSAR stochastic data are multiplicative and heteroskedastic in their natural domain.
It is hence desirable to establish additive and homoskedastic models,
  such that the benefits of homoskedastic statistical estimation framework can be demonstrated and realized for practical applications such as speckle filtering.
In addition, the processing of multi-dimensional POLSAR data requires the establishment of discrimination observables
  which are to be scalar and statistically consistent.
Moreover, these same scalar observable quantities also need to be naturally representative for the multidimensional POLSAR data.

In this thesis, the effects of homoskedasticity on SAR and POLSAR speckle filtering within the framework of computational and statistical estimation are extensively studied. 
Concurrently, the statistical behaviour of the determinant of POLSAR covariance matrix is also explored,
  where it is shown to be the representative scalar observable for the multidimensional POLSAR, similar to the role of the intensity in SAR.

As a result of these studies, several scalar statistical models based on the determinant of POLSAR covariance matrix are proposed and validated.
These generic models for POLSAR are also shown to be both multiplicative and heteroskedastic, similar to the models for SAR intensity. 
Subsequently, logarithmic transformation is applied onto both SAR and POLSAR models
  to convert them into additive and homoskedastic models.
From these models, the benefits of homoskedastic statistical estimation framework are then further explored.

There are several beneficial implications of the theory proposed in this thesis. 
Since the scalar and representative models for POLSAR extend the traditional models for SAR's intensity,
  its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
Similarly, the homoskedastic model carries additional benefits.
For inexperienced researchers (such as this author when he began this research),
  who attempt to process either SAR or POLSAR data using existing computation algorithms
  which most of the time expect an additive and homoskedastic input,
  this thesis proposes alternative and more familiar additive and homoskedastic models.
For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 
  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the statistical estimation framework for (POL)SAR.
